%!TEX root = ../report.tex
\chapter{System Context}
\label{ch:context}

We are the architecture team of the company \CompanyName. Our team is specialized in making smart systems for environmental monitoring.

<<<<<<< HEAD
\section{Context}
We are the architecture team of the company \CompanyName. Our team is specialized in making smart systems for environmental monitoring.

All around the world, natural disasters cause allot of trouble. These disasters can result in catastrophic events that causes deaths and take a huge amount of money to repair damage caused.

Floods of rivers and lakes for example, destroy huge amounts of farmlands and sometimes even causes deaths. Climate change and extreme weather phenomena cause these floods to get worse every year. This causes the damage of the floods to increase, which means that there is a great need for a system that can reduce this damage. There's a huge need for a system that will help the people during natural disasters like these, which is what this system aims to do.

%If people know that a flood is going to happen or is happening, they could anticipate on it. If they then also knew what to do, they could be able to save the lives of themselves or others. 

=======
All around the world, natural disasters cause a lot of trouble. These disasters can result in catastrophic events that cause deaths and require a huge amount of money to repair damage caused.

Climate change and extreme weather phenomena cause these floods to get worse every year. This causes the damage of the natural disasters to increase, which means that there is a great need for a system that can reduce this damage. There's a huge need for a system that will help the people during natural disasters like these, which is what this system aims to do.

%If people know that a flood is going to happen or is happening, they could anticipate on it. If they then also knew what to do, they could be able to save the lives of themselves or others. 

>>>>>>> 89462d9aed40ba89fa89bfb24af73d5802479848
The goal of our first product is to:
\begin{enumerate}
  \item Safe lives
  \item Reduce damage costs
  \item Reduce the social consequences
\end{enumerate}
<<<<<<< HEAD
In order to do this, the system tries to predict upcoming floods as correctly as possible. The system will provide warnings and guidance to the necessary people during and, if possible, before a flood. By using various kinds of sensors, vehicles and control units, this system monitors certain areas. If something suspicious is happening, the system will check and verify the information in order to not give false flood warnings. When a flood is (or will) indeed occur, the system   provides warnings and guidance to the necessary people during and, if possible, before a flood. 
=======

To achieve the aforementioned goals, the system will provide predictions with regard to upcoming floods.\\

The first release of this system that we as \CompanyName build, will only focus on floods as a natural disaster. The system will provide warnings and guidance to the necessary people during and, if possible, before a flood. By using various kinds of sensors, vehicles and control units, this system monitors certain areas. If something suspicious is happens, the system will check and verify the information in order to not give false flood warnings. When a flood is (or will) indeed occur, the system   provides warnings and guidance to the necessary people during and, if possible, before a flood. 
>>>>>>> 89462d9aed40ba89fa89bfb24af73d5802479848

When this flood monitoring system works as planned and shows that it can indeed reduce the damage of floods, new products will be made by our company that will focus on reducing the damage of other kinds of natural disasters.

Over time, the system will reduce social, financial and human losses of natural disasters, starting with floods. This will revolutionize the way we think about natural disasters. Though the market around environmental monitoring is very competitive, this system aims at being a core part of future monitoring systems by being as dynamic and flexible as possible. Thereby allowing new features to be added easily, allowing the system to grow over time, including new upcoming user needs.