%!TEX root = ../report.tex
%############################################################
%## Commercial non-functional 
%############################################################

\subsection{Commercial non-functional requirements}

\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead

    
	1 & 2 & 2 & 4 & 5 & 6 \\
	
	CNF-2 & Must & Yes & 4 & 4,6 & Fulfilled by the tested Geobead sensors quality and reliability in the market. \\
	CNF-3 & Must & Yes & 4 & 2,3,9 & Fulfilled by the table version and the SMF business plan. \\
	
    % %format:
    % ~\ref{} %nr
    % & %priority
    % & %fulfilled
    % & %Decision
    % & %Chapter
    % & %Remarks
    % \\ \midrule

    %	\reqRow{cnfr}{Must}{The system is affordable. The initial price of the system is lower than 95\%\ of the competitors price in the same market.}

    %	\reqRow{cnfr}{Must}{The expected lifetime of the sensors should be at least three years.}
    	
	% \reqRow{cnfr}{}{Must}{The system is extendable. At least four updates/versions of the system will be released.}	

    \caption{Evaluation of non-functional commercial requirements} 
    \label{table:eval-commercialNF-requirements}\\
\end{longtable}

\subsection{Technical non-functional(NF) requirements}
This subsection elaborates about technical non-functional requirements that contain reliability, availability, resilience, performance, interoperability, security, and scalability.

\subsubsection{Reliability}

\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead

    % %format:
    % ~\ref{} %nr
    % & %priority
    % & %fulfilled
    % & %Decision
    % & %Chapter
    % & %Remarks
    % \\ \midrule
    
    ~\ref{REL:sensors=reachserver} %nr
    & Must
    & Yes
    & ~
    & \ref{sec:hardware-description}
    & Fulfilled, TCP/IP connection will guarantee that data can reach the central server in 99.9\% of all cases.
    \\ \midrule

    ~\ref{REL:sensor-incorrectvalues} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:logicalview}, \ref{subsec:deploymentview}
    & Fulfilled, Sensor Manager and Abnormality algorithm will check for incorrect values.
    \\ \midrule

    ~\ref{REL:falsenegative} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:logicalview}
    & Fulfilled, algorithm guarantees that the result is always correct (no false negative).
    \\ \midrule

    ~\ref{REL:falsepositive} %nr
    & Must
    & Yes
    & ~
    & \ref{table:uc-determine-flood-probability}
    & Fulfilled, UAV will make sure false positive will not happen.
    \\ \midrule

	\caption{Evaluation of non-functional reliability requirements}
    \label{table:eval-technical-nf}\\
\end{longtable}


\subsubsection{Availability}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead

    % %format:
    % ~\ref{} %nr
    % & %priority
    % & %fulfilled
    % & %Decision
    % & %Chapter
    % & %Remarks
    % \\ \midrule

    \ref{AVA:uptime} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:availability}
    & Fulfilled, the SFM will not be down for more than 2 hours per month.
    \\ \midrule

    \ref{AVA:downtime} %nr
    & Must
    & Yes
    & ~
    & \ref{sec:hardware-overview}
    & Fulfilled, the SFM has multiple data centers that will minimize downtime.
    \\ \midrule

    \ref{AVA:forecastingservices} %nr
    & Must
    & Yes
    & ~
    &~\ref{subsec:external-system}
    & Fulfilled by the system contacting several API's to base the decisions on.
    \\ \midrule 

    \caption{Evaluation of non-functional availability requirements} 
    \label{table:eval-functional-requirements}
\end{longtable}

\subsubsection{Resilience}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead
    
    % %format:
    % ~\ref{} %nr
    % & %priority
    % & %fulfilled
    % & %Decision
    % & %Chapter
    % & %Remarks
    % \\ \midrule

    %\reqRow{RES}{recognizefail}{Must}{The system recognizes failures within half an hour}
    ~\ref{RES:recognizefail} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:logicalview}
    & Fulfilled, the system recognizes failure in each data reads which means significantly less than half an hour.
    \\ \midrule

    % \reqRow{RES}{failrecover}{Must}{The system recovers from failures without the performance or the functionality of the system being affected.}
    ~\ref{RES:failrecover} %nr
    & Must
    & Yes
    & \ref{hw:5}, \ref{hw:6}
    & \ref{sec:hardware-overview}, \ref{sec:hardware-description}
    & Fulfilled, the servers are replicated thus the system is fault-tolerant.
    \\ \midrule

    % \reqRow{RES}{backup}{Must}{All system data must be backed up every 24 hours.}
    ~\ref{RES:backup} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:database-data}
    & Fulfilled, the database is replicated which means the data is always backed up.
    \\ \midrule

    % \reqRow{RES}{backuprestore}{Must}{In case of a data loss, the data should be retrieved and restored from a backup within 2 hours.}
    ~\ref{RES:backuprestore} %nr
    & Must
    & Yes
    & ~
    & \ref{subsec:database-data}
    & Fulfilled, the database is redundant which means restoring data takes significantly less than two hours.
    \\ \midrule

    % \reqRow{RES}{backuparea}{Must}{Backup copies are stored in a location which is not in the same area as the system (50 km away).}
    ~\ref{RES:backuparea} %nr
    & Must
    & Yes
    & ~
    & \ref{sec:hardware-overview}, \ref{subsec:database-data}
    & Fulfilled, the SFM has three data centers that are located more than 50km away.
    \\ \midrule

	\caption{Evaluation of non-functional resilience requirements}
    \label{table:eval-technical-nf}\\
\end{longtable}


\subsubsection{Performance}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead

        %	\reqRow{perf}{Must}{Data is transmitted from and to the system with a minimum average speed of 10 megabits per second}
        PERF-1 & Must     & Yes  & \ref{hw:7} & \ref{sec:hardware-decisions}, \ref{sec:hardware-description} & Fulfilled, each components of the system are connected by Gigabit Ethernet. \\ \midrule

        %	\reqRow{perf}{Must}{	The data transmission between the sensors and the system is on average at least 10 megabits per second for each sensor.}
        PERF-2 & Must     & Yes  & \ref{hw:3} & \ref{sec:hardware-decisions} & Fulfilled, Arduinos that are connected to sensors send data in 10 Megabits per second. \\ \midrule

        %	\reqRow{perf}{Must}{	The time for the system to compute if there is a flood or not according to a critical level and the data received from the sensors is at most 5 minutes. }
        PERF-3 & Must     & Yes  & ~ & \ref{sec:hardware-description} & Fulfilled, analytics cluster will compute this calculation. \\ \midrule

        %	\reqRow{perf}{Must}{ If an imminent flood is detected, the warning text message to citizens arrives in 5 minutes. }
        PERF-4 & Must     & Yes  & ~ & \ref{subsec:external-system}, \ref{subsec:logicalview}         & Fulfilled, SMS service will make sure the SMS will arrive within 5 minutes. \\ \midrule

        %	\reqRow{perf}{Must}{ If an imminent flood is detected, the warning to the emergency room arrives within 1 minute. }
        PERF-5 & Must     & Yes  & ~ & \ref{subsec:external-system}, \ref{subsec:logicalview}         & Fulfilled, TCP/IP connection guarantees that the information will arrive within one minute. \\ \midrule

	\caption{Evaluation of non-functional performance requirements}
    \label{table:eval-technical-nf}\\
    \end{longtable}

\subsubsection{Interoperability}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
    \bo{Nr.} & \bo{Priority} & \bo{Fulfilled} & \bo{Decision} & \bo{Chapter} & \bo{Remarks} \\ \toprule \endhead

        Nr.    & Priority & Fulfilled & Decision & Chapter & Remarks \\ \midrule
        % \reqRow{intr}{Must}{The system is able to retrieve data from different types of water level sensors and dike sensors. Also future versions of the sensors should be supported.}
        INTR-1 & Must     & Yes      & ~\ref{dec:3} & ~\ref{sec:hardware-overview} & Fulfilled by using GeoBeads and Water level sensor. \\ \midrule
        % \reqRow{intr}{Must}{The system is able to retrieve external data from different weather forecast, demographic and geographic APIs. Also future versions of the APIs should be supported.}
        INTR-2 & Must     & Yes      & &~\ref{subsec:external-system} & Fulfilled by using several external API providers.       \\ \midrule

	\caption{Evaluation of non-functional interoperability requirements}
    \label{table:eval-technical-nf}\\
\end{longtable}
\subsubsection{Security}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}

        Nr.   & Priority & Fulfilled & Decision & Chapter & Remarks \\ \midrule
        % \reqRow{sec}{Must}{Access to the system is restricted to users, which are authorized and authenticated using a password protected user account.}
        SEC-1 & Must     & Yes      & & ~\ref{subsec:system-diagram} & Fulfilled, the user must be authorized to enter the system. \\ \midrule
        % \reqRow{sec}{Must}{All communication to, from and within the system is encrypted.}
        SEC-2 & Must     & Yes      & ~\ref{dec:9} & ~\ref{subsec:channels-information-flows} & Fulfilled, by using secure channel. \\ \midrule
        % \reqRow{sec}{Must}{User account information is stored encrypted.}
        SEC-3 & Must     & Yes      & ~\ref{dec:6} & ~\ref{subsec:database-data} & Fulfilled, applied in Elasticsearch DB. \\ \midrule
        % \reqRow{sec}{Must}{The system is protected on both the application layer and network layer.}
        SEC-4 & Must     & Yes      & & ~\ref{sec:hardware-overview} & Fulfilled, in the data center level. \\ \midrule
        % \reqRow{sec}{Must}{The system communicates with the sensors via a secure HTTPS connection.}
        SEC-5 & Must     & Yes      & ~\ref{dec:9} & ~\ref{sec:hardware-overview} & Fulfilled, by using Arduino to send data. \\ \midrule

	\caption{Evaluation of non-functional security requirements}
    \label{table:eval-technical-nf}\\
\end{longtable}

\subsubsection{Scalability}
\begin{longtable}{llllL{\tw{0.1}}L{\tw{0.4}}}
        Nr.     & Priority & Fulfilled & Decision & Chapter & Remarks \\ \midrule
        % \reqRow{scale}{Must}{The database and services of the system can scale within 1 hour, when the systems resource usage increases.}
        SCALE-1 & Must     & Yes      & ~\ref{dec:6} & ~\ref{subsec:database-data} & Fulfilled by adapting Elasticsearch. \\ \midrule
        % \reqRow{scale}{Must}{The system is configurable to run in different areas and with different sensors.}
        SCALE-2 & Must     & Yes      & & ~\ref{sec:hardware-overview} & Fulfilled by adapting multiple data centers and multiple sensor type. \\ \midrule
        % \reqRow{scale}{Must}{The system maintains the performance requirements when the number of sensors is increased and the data from sensors is expanded.}
        SCALE-3 & Must     & Unknown  & & -         & Expected, not yet tested. \\ \midrule

	\caption{Evaluation of non-functional scalability requirements}
    \label{table:eval-technical-nf}\\
\end{longtable}
