%!TEX root = ../report.tex
\chapter{Analysis}
\label{ch:analysis}

Assumptions:
\noindent{
	\begin{itemize}
	  \item People requesting guidance have access to a phone that is either connected 		to a mobile network or to the internet
	  \item The system is able to monitor various kinds of sensors
	  \item The system has access to the internet
	  \item The sensors are (in some way) connected to the system
	  \item The system is able to use various kinds of sensors in order to predict floods.
	  \item When the system has enough proof of a flood, the users will be informed in a timely manner (within 30 seconds maximal).
	  \item People within a range of (30km?) will be warned about a detected flood
	  \item The system uses multiple weather forecasting services to make its own predictions about possible upcoming floods.
	\end{itemize}
}

Decisions:
\noindent{
	\begin{itemize}
	\item Security? (What if someone tries to manipulate a sensor?)
	\item One or multiple warning systems (failover)
	\item Networking? Redundancy of cables (trunked?)
	\item When to alarm? What to do if only 1 sensor warns about a flood?
	\item Security decisions?
	\item Operating system decision
	\item Storage decision
	\item Push or pull updates? (Pushing I’m hoping)
	\item Programming language(s) for the system? Web-interface, sensor monitoring, weather forecasting system, push notification system
	\item In what ways will the system detect a flood? Sensors, UAV’s, forecasting?
	\item How to detect a flood based on the forecasting? Warn beforehand? Pay extra attention to the new upcoming flood by sending extra robots/uav's?
	\end{itemize}
}

%Clean decision table:
%\begin{tabularx}{\textwidth}{ l l }
%    \textbf{Name} & \textbf{Linux} \\ \hline
%    \textbf{Decision} & \textbf{1} \\ \hline \hline
%    \textbf{Status} & \textbf{New} \\ \hline
%    \textbf{Decision} &  \\ \hline
%    \textbf{Alternatives} & \\ \hline
%    \textbf{Arguments} & \\ \hline
%\end{tabularx}

\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
    \textbf{Name} & \textbf{Linux} \\ \hline
    \textbf{Decision} & \textbf{\nextNrRef{dn}} \\ \hline \hline
    \textbf{Status} & \textbf{New} \\ \hline
    \textbf{Problem/Issue} & The warning system software for the natural disasters need a platform to work on.  \\ \hline
    \textbf{Decision} &  The warning system will use Linux as a platform\\ \hline
    \textbf{Alternatives} & \cellBox{\textit{Linux}\\ Linux is a free platform that has proven itself and is used by many servers. It is reliable and more secure. } \\ \hline
    \textbf{Arguments} & \cellBox{} \\ \hline
\end{tabular}