%!TEX root = ../report.tex
\section{Stories and use-cases}
\subsection{A citizen receives a warning about an upcoming flood}
\textbf{Scope:} Warning part of the system\\\\
\textbf{Level:} Main process\\\\
\textbf{Primary actor:} Citizen\\\\
\textbf{Stakeholders and interests:}\\
	1. Government - the government wants to warn the citizens in case of a flood \\
	2. Citizens - citizens want to be warned in case of a flood \\\\
\textbf{Precondition:} There is an upcoming flood and the citizens are not warned\\
\textbf{Postcondition:} There is a flood and the citizens are warned\\\\
\textbf{Main succes scenario:} \\
1 - There is the threat of an upcoming flood.\\
2 - A warning mechanism is triggered.\\
3 - The authorities are warned about the upcoming flood.\\
4 - The authorities use their systems to warn the citizens.\\
5 - The citizens are warned and can move to a safer place.\\\\
\textbf{Extensions:} \\
2a - The flood doesn't get to dangerous, it retreats. No warning mechanism is triggered.

\subsection{A citizen requests guidance to get to a safe place in a flooded area}
\textbf{Scope:} Guidance part of the system\\\\
\textbf{Level:} Main process\\\\
\textbf{Primary actor:} Citizen\\\\
\textbf{Stakeholders and interests:}\\
	1. Government - the government wants to guide the citizens to a safe place in case of a flood. \\
	2. Citizens - citizens want to be guided to a safe place in case of a flood. \\\\
\textbf{Precondition:} There is a flood and the citizen wants guidance to a safe place. \\
\textbf{Postcondition:} Citizen is guided to a safe place. \\\\
\textbf{Main succes scenario:} \\
1 - There is a flood going on.\\
2 - A citizen requests guidance to a safe place.\\
3 - The citizen gets guidance through a smartphone.\\
4 - The citizen makes it to the safe place.\\\\
\textbf{Extensions:} \\
3a - Smartphone has no internet connection, provide latest information available.\\
3b - GPS of smartphone doesn't work, provide the citizen with the right information to make decisions by himself.\\
4a - Citizen can't make it to the safe place. Provide the citizen with a route to an alternative safe place.

%If we decide to use user input
\subsection{A citizen reports an obstruction}
\textbf{Scope:} Monitoring part of the system\\\\
\textbf{Level:} Main process\\\\
\textbf{Primary actor:} Citizen\\\\
\textbf{Stakeholders and interests:}\\
	1. Citizen - A citizen wants to report an obstruction to make the guidance part more reliable. \\\\
\textbf{Preconditions:} There is an obstruction which is not yet reported. \\
\textbf{Postconditions:} There is an obstruction which is reported by a citizen and is known in the system. \\\\
\textbf{Main succes scenario:} \\
1 - There is an obstruction somewhere in the area. \\
2 - The citizen opens our application on his smartphone. \\
3 - The citizen reports the kind of obstruction and the location. \\
4 - The system gets the obstruction information as input. \\
5 - The obstruction is processed in the system and visible to other citizens. \\\\
\textbf{Extensions:} \\
3a - The citizen doesn't know the location, GPS can be used in this case. If GPS doesn't work, the obstruction can't be reported. \\
4a - The smartphone can't send the information. In this case, the obstruciton can't be reported. 
