%!TEX root = ../report.tex
\section*{Authors}

\begin{tabular}{L{\tw{0.45}} L{\tw{0.45}}}
    \textbf{Name} & \textbf{E-Mail} \\ \toprule
	Eedema, Gerrit & G.Eedema@student.rug.nl\\
	Putra, Guntur & G.D.Putra@student.rug.nl\\
	Fakambi, Aur\'{e}lie & A.Fakambi@student.rug.nl\\
	Schaefers, Joris & J.Schaefers@student.rug.nl\\
	Brandsma, Jeroen & J.T.Brandsma@student.rug.nl\\
	Menninga, Wouter & W.G.Menninga@student.rug.nl\\ 
	(Klinkenberg, Guus & G.Klinkenberg@student.rug.nl)\\ \bottomrule
\end{tabular}

\section*{Revision History}

\begin{longtable}{L{\tw{0.1}} L{\tw{0.2}} L{\tw{0.1}} L{\tw{0.5}}}
    \textbf{Version} & \textbf{Author} &  \textbf{Date} & \textbf{Description}\\

    \toprule
    % 1st week
    0.1 & all & 06-09-15 & Setting up the working environment and the initial document structure. Draft versions of the first four chapters created, which are (respectively) Context, Architectural business information, Requirements and Analysis. \\
    \midrule

    % 2nd week
    0.2 & Menninga, ...     & 10-09-15 & First version of functional requirements \\
    
        & Schaefers \& Eedema   & 13-09-15 & Changed the context and enhanced the business information  \\

        & Brandsma          & 13-09-15 & Updated the requirements part \\
        & Putra            & 13-09-15 & Updated the stakeholder of requirements part \\
    \midrule

    % 3rd week
    0.3 & Menninga          & 17-09-15 & Updated the functional requirements \\
        & Brandsma          & 17-09-15 & Updated architectural vision and use-cases\\
        & Klinkenberg \& Eedema & 17-09-15 & Updated technical requirements, some formatting, started work on the first two decisions\\
        & Menninga          & 19-09-15 & Added and updated functional requirements \\
        & Putra             & 19-09-15 & Processed feedback, revised the stakeholder, and added decision on database selection.\\
        & Eedema            & 19-09-15 & Processed feedback \\
        &                   & 19-09-15 & Improved business chapter \\
        & Menninga          & 20-09-15 & Updated assumptions and improvements to structure of analysis chapter. Added decision about type of water level sensor. \\
        & Brandsma          & 20-09-15 & Updated requirements chapter. Added decision about cloud computing.\\
        & Schaefers         & 20-09-15 & Improved business chapter and processed feedback. Checked the use cases and put them in tables.\\
    \midrule

    % 4th week
    0.4 & Menninga  & 23-09-15 & Improved functional requirements after feedback  \\
        & Brandsma  & 24-09-15 & Revised architectural vision, extended and improved use-cases \\
        & Menninga  & 24-09-15 & Changed layout of the risk assessment section \\
        &           & 24-09-15 & Changed layout of the risk assessment section \\
        & Fakambi   & 24-09-15 & Improvements to the non-functional requirements \\
        & Eedema    & 24-09-15 & Improvements to the business part \\
        & Putra     & 24-09-15 & Improved stakeholder with new quality attributes. \\
        &           &          & Added key-drivers after stakeholder. \\
        & Menninga  & 26-09-15 & Complemented and improved non-functional requirement section \\
                    &          &          & Removed some obsolete functional requirements \\
                    &          &          & Improved risk assessment section \\
        & Putra     & 26-09-15 & Business rationale. \\
        &           & 27-09-15 & Draft chapter 5,6, and 7.\\
        & Brandsma  & 27-09-15 & Improved some figures. Improved chapter 4. Reviewing. \\
    \midrule

    % 5th week
    0.5 & Putra     & 30-09-15 & Hardware architecture draft.  \\
    0.5 & Menninga  & 30-09-15 & Changed Use Case diagram. Improved and added use cases \\
        &           &          & Added High Level Requirements \\
        &           &          & Updated stake holders (added weights) and changed key drivers accordingly \\
        &           &          & Small improvements to the non-functional requirements \\
        &           &          & Changed the evolution requirements \\
        &           &          & Added a risk about 3rd parties not developing apps \\
        & Eedema    & 01-10-15 & Worked on chapter 5 \\
        & Brandsma  & 01-10-15 & Worked on chapter 5 \\
    0.5 & Menninga  & 03-10-15 & Added decision about dike sensors (and connectivity) \\
    0.5 & Menninga  & 04-10-15 & Small updates to chapter 3, added glossary \\
        & Putra     & 04-10-15 & Added decision on main analytics servers, database servers, and switches \\
        &           &          & Added hardware description of main analytics servers and database servers. \\
        & Menninga  & 04-10-15 & Changed hardware overview diagram \\
	\midrule
    % 6th week
    0.6 & Menninga  & 08-10-15 & Updated hardware costs ch. 2 + improvements ch. 3 \\
        &           &          & Added activity diagram for flood monitoring / warning \\
        & Eedema    & 08-10-15 & Updated chapter 5 + logical view \\
        & Brandsma  & 08-10-15 & Updated chapter 5 + logical view \\
        & Putra     & 08-10-15 & Updated figures of cluster on chapter 6.\\
        &           &          & Added deployment view of software architecture.\\
        & Menninga  & 11-10-15 & Updated use case about warning citizens \\
        &           &          & Added sequence diagrams for sending data and warnings \\
        &           &          & Updated dikes sensors information \\
        & Putra     & 11-10-15 & Updated figures of cluster on chapter 6.\\
        &           & 11-10-15 & Updated figure of hardware overview on chapter 6.\\
        &           & 11-10-15 & Updated figure of deployment view diagram on chapter 7.\\
        & Eedema    & 11-10-15 & Setup chapter 8.\\
        % &           & 11-10-15 & Added artifacts for deployment view on chapter 7.\\
    
    % 7th week
    \bottomrule
\end{longtable}